Deployable Probabilistic Programming

### 2019-04-16 paper/paper.tex
more citations

	There are two polar views on the role of probabilistic
	programming.  One view is that probabilistic programming is
	a flexible framework for specification and analysis of
	statistical models.  Proponents of this view perceive
	probabilistic programming as a tool for data science
	practitioners. A typical workflow consists of data
	acquisition and pre-processing, followed by several
	iterations of exploratory model design and testing of
	inference algorithms. Once a sufficiently robust statistical
	model is obtained, analysis results are post-processed,
	visualized, and occasionally integrated into algorithms of a
	production software system.

@@

	Our attitude differs from the established approach in that
	instead of proposing yet another probabilistic programming
	language, either genuinely different~\cite{MMR+07,Stan17} or derived from
	an existing general programming language by extending the
	syntax or changing the semantics~\cite{GMR+08,TMY+16,GXG18}, we advocate
	enabling probabilistic inference on models written in a
	general probabilistic programming language, the same one as
	the language used to program the bulk of the system. We
	formulate guidelines for such implementation, and based on
	the guidelines, introduce a probabilistic programming
	facility for the Go programming language. By explaining our
	design choices and implementation techniques, we argue that
	a similar facility can be added to any modern general
	purpose programming language, giving a production system
	modeling and inference capabilities which do not fall short
	from and sometimes exceed those of probabilistic programming
	centric systems with custom languages and runtimes.

>>>>

	There are two polar views on the role of probabilistic
	programming.  One view is that probabilistic programming is
	a flexible framework for specification and analysis of
	statistical models~\cite{WSG11,TMY+16,GXG18}. Proponents of
	this view perceive probabilistic programming as a tool for
	data science practitioners. A typical workflow consists of
	data acquisition and pre-processing, followed by several
	iterations of exploratory model design and testing of
	inference algorithms. Once a sufficiently robust statistical
	model is obtained, analysis results are post-processed,
	visualized, and occasionally integrated into algorithms of a
	production software system.

@@

	Our attitude differs from the established approach in that
	instead of proposing yet another probabilistic programming
	language, either genuinely different~\cite{MMR+07,Stan17} or derived from
	an existing general programming language by extending the
	syntax or changing the semantics~\cite{GMR+08,TMY+16,GXG18}, we advocate
	enabling probabilistic inference on models written in a
	general probabilistic programming language, the same one as
	the language used to program the bulk of the system. We
	formulate guidelines for such implementation, and based on
	the guidelines, introduce a probabilistic programming
	facility for the Go programming language~\cite{Golang}. By
	explaining our design choices and implementation techniques,
	we argue that a similar facility can be added to any modern
	general purpose programming language, giving a production
	system modeling and inference capabilities which do not fall
	short from and sometimes exceed those of probabilistic
	programming centric systems with custom languages and
	runtimes.
